---
title: "Final project"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
---

```{r}
library(tidyverse)
library(stringr)
library(httr)
library(rvest)
library(lubridate)
library(ggmap)
library(shiny)
library(shinythemes)
library(usdata)
library(maps)
library(grDevices)
library(flexdashboard)
library(ggmosaic)
library(RColorBrewer)
```


```{=html}
<style>                     
.navbar {
  background-color: black;
  border-color: white;
  menu-color:white
}

</style>
```
# About {data-navmenu="Menu"}

## Column {data-width = 400}

#### Authors

Lance Nemecek and Peter Gao

#### Background Information
About the TRFFS website: The TRFFS is a website where people can see the college track & field rankings and results.

We require the names of all MIAC athletes and their event times. The TFRRS website provides data back to 2015 so we can analyze data for the past 9 years of MIAC competition. We intend to use the shiny package to organize our findings in an easy to operate manner for a viewer of our website. Our key variables are the following: 

+ Athlete Name
+ Athlete School
+ Athlete time 
+ Distance
+ Date of Race
+ Finishing Position

These 5 variables will provide the necessary information we need for our analysis. 


#### Data Soures
+ Data from [TFRRS](https://www.tfrrs.org/) 
+ Data we will use in our final project from (https://www.tfrrs.org/lists/4723/MIAC_Outdoor_Performance_List)

#### Investigate Questions

+ Which schools are the best at each event?
+ Has the MIAC improved as the years progressed? 
+ How does each class year perform in college?
+ Does athletes with the top marks finish as expected?

# Which schools are the best at each event? {data-navmenu="Menu"}

## Column {data.height = 700}

Which schools are the best at each event?


In this question, we will consider the number of athletes from each school in the top 30 in the 100-meter event to determine which school is stronger. That is, if a school has the most athletes in the top thirty, then that school is best at the event.



### Select Input
```{r, fig.height=4}
inputPanel(selectInput("event", label = "Select Event",
                       choices = c("100","200", "400", "800", "1500","5000", "10000", "100 Hurdles","400 Hurdles", "3000 SteepLechase", "4*100 Relay","4*400 Relay","High Jump","Pole Vault", "Long Jump", "Triple Jump","shot Put", "Discus", "Hammer", "Javelin", "Heptathlon"), selected = "All"))
          
inputPanel(selectInput("bars", label = "Select Years",
                       choices = c(2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024), selected = 5))

```


Column 
-------------------------


Note that 4*100 and 4*400 should be considered separately.
Column 
-------------------------





# Has the MIAC improved as the years progressed? {data-navmenu="Menu"}

## Inputs {.sidebar}

```{r}

```

```{r}
p("")
```

## Column

### Figure 1

```{r, fig.height=4, fig.width=4}

```

### Figure 2

```{r}

```

# How does each class year perform in college? {data-navmenu="Menu"}

## Column

```{r}

```

### section 1

```{r, fig.height = 3}

```

### section 2

```{r, fig.height=4}

```

## Column

### section 2

```{r, fig.height = 3}

```

### Commentary

```{r}
p("." )
```

# Does athletes with the top marks finish as expected? {data-navmenu="Menu"}

## Column

```{r}

```

### section1

```{r}

```

### section2

```{r}

```

## Column

### Commentary

```{r}
p("")
```

### section 3

```{r}

```

### section4

```{r}

```

# potential question ? {data-navmenu="Menu"}

## Column

# Discussion {data-navmenu="Menu"}
