---
title: "Final project"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
---

```{r}
library(tidyverse)
library(stringr)
library(httr)
library(rvest)
library(lubridate)
library(ggmap)
library(shiny)
library(shinythemes)
library(usdata)
library(maps)
library(grDevices)
library(flexdashboard)
library(ggmosaic)
library(RColorBrewer)
```


```{=html}
<style>                     
.navbar {
  background-color: black;
  border-color: white;
  menu-color:white
}

</style>
```
# About {data-navmenu="Menu"}

## Column {data-width = 400}

#### Authors

Lance Nemecek and Peter Gao

#### Background Information

The MIAC, also known as the "Minnesota Intercollegiate Athletic Conference," represents a collection of small Division III schools scattered across the state of Minnesota. Our project entails an investigation into the performance of the MIAC track and field conference from 2015 to 2024. To address this inquiry, we utilize data extracted from TFRRS, the "Track and Field Results Reporting System." We compile data from all collegiate track and field events, analyzing the top 30 scores in every event each year. Our analysis is centered around four key questions:

1. Which schools excel in each event?
2. Has the performance of the MIAC improved over the years?
3. How do athletes from different class years perform in college?
4. Does wind significantly impact athletes' performance?

Our research aims to provide valuable insights for current athletes seeking to enhance their understanding of the sport, as well as serve as an informative resource for high school students and parents interested in learning more about this specialized discipline.


#### Data Soures
+ Data from [TFRRS](https://www.tfrrs.org/) 
+ Data we will use in our final project from https://www.tfrrs.org/lists/4723/MIAC_Outdoor_Performance_List

# Which schools are the best at each event? {data-navmenu="Menu"}

## Column {data.height = 700}

Which schools are the best at each event?


In this question, we will consider the number of athletes from each school in the top 30 in the 100-meter event to determine which school is stronger. That is, if a school has the most athletes in the top thirty, then that school is best at the event.

``````{r, echo = FALSE}
all_running_events = read_rds("AllRunningEvents.csv")
```


```{r, echo = FALSE}
all_running_events <- all_running_events %>%
    mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))
```


### Select Input
```{r, echo = FALSE}
inputPanel(
  selectInput(inputId = "categ",
              label = h3("Event"),
              choices = c("one_hundred", "two_hundred", "four_hundred", "eight_hundred", "fifteen_hundred", "five_k", "ten_k", "one_ten_hurdles", "four_hundred_hurdles", "steeplechase"),
              selected = "one_hundred"),
  
  selectInput(inputId = "categ1",
              label = h3("Year"),
              choices = c("2024", "2023", "2022", "2021", "2019", "2018", "2017", "2015"),
              selected = "2024")
)
```

```{r, echo = FALSE}
testall_running_events <- all_running_events |>
  pivot_wider(names_from = event,
              values_from = school)
view(testall_running_events)
```


Column 
-------------------------
### Select Input

```{r, echo = FALSE}
renderPlot({
  filtered_data <- testall_running_events |>
    filter(!is.na(.data[[input$categ]]), year(date) == as.numeric(input$categ1))

  ggplot(filtered_data, aes(x = .data[[input$categ]])) +
    geom_bar(fill = "lightblue", color = "black", alpha = 0.7) +
    labs(title = "Distribution of Events",
         x = "Event",
         y = "Frequency") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_fill_manual(values = c("lightblue", "green"))  
})

```

### Commentary

```{r}
p("St. Olaf has consistently been the dominant distance running school in the MIAC. The Oles consistently field over 5 runners each year for the steeplechase, 5k, and 10k. There isn't a dominant school for the 1500 or 800 meters; this makes sense since schools with both strong distance runners and sprinters will typically have a solid group who can excel across various distances. While St. John's and St. Thomas both have a respectable number of sprinters, Bethel remains the most dominant in sprinting events. They lead almost every year in the 200, 400, 110 hurdles, and 400 hurdles.
" )
```




# Has the MIAC improved as the years progressed? {data-navmenu="Menu"}

To determine how has the MIAC improved as the years progressed, we can measure how the champion for each event perform each year. That is, we are making a scatterplot with line, which x-axis is year from 2015 to 2024, and the y-axis is the time or meters due to different events.

Column 
-------------------------
In the following plots, we are measuring the performance of champions in events that measure their results in seconds.

```{r, include = FALSE}
testall_running_events <- all_running_events |>
  pivot_wider(names_from = event,
              values_from = school)
view(testall_running_events)
```


```{r, fig.height=4}
inputPanel(
  selectInput(inputId = "champs",
              label = h3("Running Events"),
              choices = c("one_hundred", "two_hundred", "four_hundred", "eight_hundred", "fifteen_hundred", "five_k", "ten_k", "one_ten_hurdles", "four_hundred_hurdles", "steeplechase"),
              selected = "one_hundred"))
```

```{r, echo=FALSE}
renderPlot({
  testall_running_events |>
    filter(seed == 1, !is.na(.data[[input$champs]])) |>
    ggplot(aes(x = year_date, y = time)) +
    geom_point() +
    labs(x = "Year", y = "Times", title = "Progression of MIAC Relays") +
    theme_minimal()
})

```

```{r}
all_relays = read_rds("AllRelays.CSV")
```

```{r, echo = FALSE}
all_relays <- all_relays %>%
    mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))
```


```{r, fig.height=3}
inputPanel(
  selectInput(inputId = "relays",
              label = h3("Relays"),
              choices = c("4x100", "4x400"),
              selected = "4x100"))
```

```{r, echo = FALSE}
all_relays <- all_relays |>
  pivot_wider(names_from = event,
              values_from = meet)
view(all_relays)
```



```{r, echo=FALSE}
renderPlot({
  all_relays |>
    filter(seed == 1, !is.na(.data[[input$relays]])) |>
    ggplot(aes(x = year_date, y = time)) +
    geom_point() +
    labs(x = "Year", y = "Times", title = "Progression of MIAC Relays") +
    theme_minimal()
})
```

```{r, echo = FALSE}
all_field_events = read_rds("AllFieldEvents.csv")
```

```{r, echo = FALSE}
all_field_events <- all_field_events %>%
    mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))
```

```{r, echo = FALSE}
testall_field_events <- all_field_events |>
  pivot_wider(names_from = event,
              values_from = meet)
view(testall_field_events)
```


```{r, fig.height=2}
inputPanel(
  selectInput(inputId = "field",
              label = h3("Field Events"),
             choices = c("High Jump","Pole Vault", "Long Jump", "Triple Jump","Shot Put", "Discus", "Hammer", "Javelin"),
              selected = "High Jump"))
```

```{r, echo=FALSE}
renderPlot({
  testall_field_events |>
    filter(seed == 1, !is.na(.data[[input$field]])) |>
    ggplot(aes(x = year_date, y = mark)) +
    geom_point() +
    labs(x = "Year", y = "Meters", title = "Field Events") +
    theme_minimal()
})
```

```{r}
tags$h1("Decathalon")
```

```{r}
combined_tableDecathlon = read_rds("Decathalon.CSV")
```

```{r}
combined_tableDecathlon<- combined_tableDecathlon %>%
    mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))
```

```{r, echo=FALSE}
combined_tableDecathlon |>
  filter(seed == 1)|>
  ggplot(aes(x = year_date, y = points)) +
  geom_point() +
  labs(x = "Year", y = "points", title = "MIAC Decathlon") +
  theme_minimal()
```

### Commentary

```{r}
p("The progression of the MIAC is different for every event, which is to be expected. There are some years where the points seem like outliers, most of the time this is due to an all american qualifier. An “All American” is an athlete who is ranked in the top 22 of the entire country in his event. Some notable all americans are the Bethel Royals 2024 4x4 relay where they are ranked #1 in the county. In 2021 St. Olaf's Steve Peper was an all American in the Decathlon. There is no clear trend for sprints, distance, or field events as a whole.  " )
```


# How does each class year perform in each college? {data-navmenu="Menu"}

In this question, we will filter each class year, and see how they perform in different events in different years. To measure how they perform, we will examine the average seed rank for each events. 

```{r, echo = FALSE}
#| include: FALSE
library(tidyverse)
library(stringr)
library(rvest)
library(httr)
```

```{r, echo = FALSE}
all_running_events = read_rds("AllRunningEvents.csv")
all_field_events = read_rds("AllFieldEvents.csv")
```

```{r, echo = FALSE}
all_running_events <- all_running_events %>%
    mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))
```

How does each class year preform?(runing events)


```{r, include = FALSE}
avg_place <- all_running_events |>
  filter(!is.na(class_year) & class_year != "") |>
  complete(year_date, class_year, fill = list(seed = NA)) |>
  group_by(class_year, year_date) |>
  summarize(avg_place = mean(seed, na.rm = TRUE))
avg_place
```

```{r, echo = FALSE}
inputPanel(
  selectInput(inputId = "avgplace",
              label = h3("class_Year"),
              choices = c("FR-1", "SO-2", "JR-3", "SR-4"),
              selected = "FR-1"))
```


```{r, echo = FALSE}
renderPlot({
  avg_place |>
    filter(class_year == input$avgplace) |>
    ggplot(aes(x = year_date, y = avg_place)) +
    geom_point(color = "skyblue") +
    geom_smooth(method = "lm", se = FALSE, color = "green", alpha = .1) + 
    theme_minimal()
})
```


```{r, include = FALSE}
class_count <- all_running_events |>
  complete(year_date, class_year, fill = list(seed = NA)) |>
  group_by(year_date, class_year) |>
  summarize(total_participants = sum(n_distinct(name)))|>
  slice(-1)
```

```{r, echo = FALSE}
inputPanel(
  selectInput(inputId = "classcount",
              label = h3("class_Year"),
              choices = c("FR-1", "SO-2", "JR-3", "SR-4"),
              selected = "FR-1"))
```


```{r, echo = FALSE}
renderPlot({
  class_count |>
    filter(class_year == input$classcount) |>
    ggplot(aes(x = year_date, y = total_participants)) +
    geom_point(color = "skyblue") +
    geom_smooth(method = "lm", se = FALSE, color = "green", alpha = .1) + 
    theme_minimal()
})
```

How does each year perform in college(field events)
```{r, include = FALSE}
all_field_events <- all_field_events |>
    mutate(date = mdy(date)) |>
    mutate(year_date = year(date))
```

```{r, include = FALSE}
avg_place2 <- all_field_events %>%
  filter(!is.na(class_year) & class_year != "") %>%
  complete(year_date, class_year, fill = list(seed = NA)) %>%
  mutate(seed = as.numeric(seed)) %>%  
  group_by(class_year, year_date) %>%
  summarize(avg_place = mean(seed, na.rm = TRUE), .groups = "drop")
avg_place2
```


```{r, include = FALSE}
class_count2 <- all_field_events |>
  complete(year_date, class_year, fill = list(seed = NA)) |>
  group_by(year_date, class_year) |>
  summarize(total_participants = sum(n_distinct(name)))|>
  slice(-1)
```

```{r, echo = FALSE}
inputPanel(
  selectInput(inputId = "avgplace2",
              label = h3("class_Year"),
              choices = c("FR-1", "SO-2", "JR-3", "SR-4"),
              selected = "FR-1"))
```


```{r, echo = FALSE}
renderPlot({
  avg_place2 |>
    filter(class_year == input$avgplace2) |>
    ggplot(aes(x = year_date, y = avg_place)) +
    geom_point(color = "skyblue") +
    geom_smooth(method = "lm", se = FALSE, color = "green", alpha = .1) + 
    theme_minimal()
})
```

```{r, echo = FALSE}
inputPanel(
  selectInput(inputId = "classcount2",
              label = h3("class_Year"),
              choices = c("FR-1", "SO-2", "JR-3", "SR-4"),
              selected = "FR-1"))
```


```{r, echo = FALSE}
renderPlot({
  class_count2 |>
    filter(class_year == input$classcount2) |>
    ggplot(aes(x = year_date, y = total_participants)) +
    geom_point(color = "skyblue") +
    geom_smooth(method = "lm", se = FALSE, color = "green", alpha = .1) + 
    theme_minimal()
})
```

### Commentary

```{r}
p("Division III sports have undergone a transformation since 2020. What was once a platform for talented but not necessarily exceptional high school runners to enhance their skills has gradually diverged from the traditional essence of Division III running. Since 2015, the freshman and sophomore classes have exhibited notable improvement, not only in terms of increased qualification rates within the top 30 for each event group but also in achieving higher placements within their respective categories. Conversely, the senior class has experienced a gradual decline, both in the quantity of participants ranked within the top 30 and their final placements.  " )
```

# How wind influence athletes performance? {data-navmenu="Menu"}

```{r}
all_running_wind_events = read_rds("AllRunningWindEvents.csv")
combined_tableTripleJump = read_rds("AllfieldWindEvents.csv")
```


```{r, include = FALSE}
all_running_wind_events <- all_running_wind_events |>
    mutate(date = mdy(date)) |>
    mutate(year_date = year(date))
```




```{r, echo = FALSE}
inputPanel(
  selectInput(inputId = "categ4",
              label = h3("Event"),
              choices = c("one_hundred", "two_hundred", "one_ten_hurdles"),
              selected = "one_hundred"),
  
  selectInput(inputId = "categ5",
              label = h3("Year"),
              choices = c("2024", "2023", "2022", "2021", "2019", "2018", "2017", "2015"),
              selected = "2024")
)
```

```{r, echo = FALSE}
renderPlot({
  all_running_wind_events |>
    filter(year_date == input$categ5, event == input$categ4) |>
    ggplot(aes(x = wind, y = time)) +
    geom_point(color = "skyblue") +
    geom_smooth(method = "lm", se = FALSE, color = "green", alpha = .1) + 
    theme_minimal()
})
```

Triple Jump
```{r, include = FALSE}
combined_tableTripleJump<- combined_tableTripleJump |>
    mutate(date = mdy(date)) |>
    mutate(year_date = year(date))
```

```{r, echo = FALSE}

inputPanel(
  selectInput(inputId = "categ6",
              label = h3("Year"),
              choices = c("2024", "2023", "2022", "2021", "2019", "2018", "2017", "2015"),
              selected = "2024")
)
```

```{r, echo=FALSE}
renderPlot({
combined_tableTripleJump |>
   filter(year_date == input$categ6) |> 
   ggplot(aes(x = wind, y = mark)) +
   geom_point() +
   geom_smooth(method = "lm", se = FALSE, color = "green", alpha = .1) + 
    theme_minimal()
    
})
```
### Commentary

```{r}
p("In sprinting events, workers are tasked with measuring the wind speed. If the tailwind is excessively strong, the sprinter's time is disqualified from records or qualifying for conference or national meets. Conversely, if there is a headwind, athletes receive deductions of fractions of seconds from their time as compensation for the handicap. Negative values on the x-axis denote a headwind, while positive values indicate a tailwind. Analysis of data from 2021 to 2024 reveals that despite other variables such as athlete speed, there appears to be a positively sloping trend line, indicating that wind may not exert as significant an influence on runner speed as previously assumed.

 " )
```

# Discussion {data-navmenu="Menu"}

Discussion:
This analysis of the MIAC running performances has given sight into the competition of Minnesota running and a sample of the trend across all division three schools and conferences. Many factors come into play with all of these plots but we will include some of the notable findings in this area.

The progression of the freshman and sophomore classes:
As noted before 


