---
title: "Final project"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
---

```{r}
library(tidyverse)
library(stringr)
library(httr)
library(rvest)
library(lubridate)
library(ggmap)
library(shiny)
library(shinythemes)
library(usdata)
library(maps)
library(grDevices)
library(flexdashboard)
library(ggmosaic)
library(RColorBrewer)
```

Read our data here!

```{r}

```

```{=html}
<style>                     
.navbar {
  background-color: black;
  border-color: white;
  menu-color:white
}

</style>
```
# About {data-navmenu="Menu"}

## Column {data-width = 400}

#### Authors

Lance Nemecek and Peter Gao

#### Background Information
About the TRFFS website: The TRFFS is a website where people can see the college track & field rankings and results.

We require the names of all MIAC athletes and their event times. The TFRRS website provides data back to 2015 so we can analyze data for the past 9 years of MIAC competition. We intend to use the shiny package to organize our findings in an easy to operate manner for a viewer of our website. Our key variables are the following: 

+ Athlete Name
+ Athlete School
+ Athlete time 
+ Distance
+ Date of Race
+ Finishing Position

These 5 variables will provide the necessary information we need for our analysis. 


#### Data Soures
+ Data from [TFRRS](https://www.tfrrs.org/) 
+ Data we will use in our final project from (https://www.tfrrs.org/lists/4723/MIAC_Outdoor_Performance_List)



# Which schools are the best at each event? {data-navmenu="Menu"}
box plot
## Column {data.height = 700}

###Figure 1

### Figure 2

## Column

### Select Input

### Comment

```{r}
p(".")
```

### Figure 3

```{r}

```

# Has the MIAC improved as the years progressed? {data-navmenu="Menu"}

## Inputs {.sidebar}

```{r}

```

```{r}
p("")
```

## Column

### Figure 1

```{r, fig.height=4, fig.width=4}

```

### Figure 2

```{r}

```

# How does each class year perform in college? {data-navmenu="Menu"}

## Column

```{r}

```

### section 1

```{r, fig.height = 3}

```

### section 2

```{r, fig.height=4}

```

## Column

### section 2

```{r, fig.height = 3}

```

### Commentary

```{r}
p("." )
```

# Does athletes with the top marks finish as expected? {data-navmenu="Menu"}

## Column

```{r}

```

### section1

```{r}

```

### section2

```{r}

```

## Column

### Commentary

```{r}
p("")
```

### section 3

```{r}

```

### section4

```{r}

```

# potential question ? {data-navmenu="Menu"}

## Column

# Discussion {data-navmenu="Menu"}
