---
title: "Questing 2 testing"
runtime: shiny
output: html_document
---
# Has the MIAC improved as the years progressed? {data-navmenu="Menu"}

To determine how has the MIAC improved as the years progressed, we can measure how the champion for each event perform each year. That is, we are making a scatterplot with line, which x-axis is year from 2015 to 2024, and the y-axis is the time or meters due to different events.

Column 
-------------------------
In the following plots, we are measuring the performance of champions in events that measure their results in seconds.

### Select Input
```{r, fig.height=3}
inputPanel(selectInput("event", label = "Select Event",
                       choices = c("100","200", "400", "800", "1500","5000", "10000", "100 Hurdles","400 Hurdles", "3000 SteepLechase", "4*100 Relay","4*400 Relay"), selected = "All"))
```

### plot 1




Column 
-------------------------
Now, in the following plots, we are measuring the performance of champions in events that measure their results in meters.

### Select Input
```{r, fig.height=3}
inputPanel(selectInput("event", label = "Select Event",
                       choices = c("High Jump","Pole Vault", "Long Jump", "Triple Jump","shot Put", "Discus", "Hammer", "Javelin", "Heptathlon"), selected = "All"))
```

### plot 2

