---
title: "Questing 3 testing"
runtime: shiny
output: html_document
---
```{r}
#| include: FALSE
library(tidyverse)
library(stringr)
library(rvest)
library(httr)
```


```{r}
write_rds(all_running_events, "AllRunningEvents.csv")
```

```{r}
all_running_events = read_csv("AllRunningEvents.csv")
```

```{r}
all_running_events <- all_running_events %>%
    mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))
```




```{r, include = FALSE}

all_running_events$time <- as.numeric(as.character(all_running_events$time))
```



```{r}
test_running_events2<- all_running_events|>
  group_by(class_year,event, year_date)|>
  mutate(time = as.numeric(time))|>
  summarize(average_time = mean(time, na.rm = TRUE))
```
```{r}
# Group data by class year, events and calculate the mean place

 
# Create a bar plot
ggplot(test_running_events2 , aes(x = year_date, y = avg_time, fill = class_year)) +
  geom_line() +
  labs(title = "Average Place by Class Year",
       x = "Class Year",
       y = "Average Place") +
  theme_minimal()
```

# How does each class year perform in college? {data-navmenu="Menu"}

In this question, we will filter each class year, and see how they perform in different events in different years. To measure how they perform, we will examine the average seed rank for each events and in each college. To do this, I will make x-axis each class year, and y-axis their resule.

Column 
-------------------------
In the following plots, we are measuring the performance of champions in events that measure their results in seconds.

### Select Input
```{r, fig.height=3}
inputPanel(
  selectInput(inputId = "categ",
              label = h3("Event"),
             choices = c("one_hundred", "two_hundred", "four_hundred", "eight_hundred", "fifteen_hundred", "five_k", "ten_k", "one_ten_hurdles", "four_hundred_hurdles", "steeplechase"),
              selected = "one_hundred"),
 selectInput(inputId = "categ1",
              label = h3("Year"),
              choices = c("2024", "2023", "2022", "2021", "2019", "2018", "2017", "2015"),
              selected = "2024"),
  selectInput(inputId = "categ2",
              label = h3("School"),
              choices = c("Augsburg", "Bethel(Minn.)", "Carleton", "Concordia-Moorhead","Gustavus Adolphus", "Hamline", "Macalester", "Saint Mary's (Minn.)", "St. Benedict", "St. Catherine(Minn.)", "St. Hohn's(Minn.)", "St. Olaf", "St. Scholastica"),
              selected = "Augsburg")
)

```

### The plot of the time of champions in 100,200, 400, 800, 1500,5000, 10000, 100 Hurdles,400 Hurdles, 3000 SteepLechase

```{r, echo=FALSE}
renderPlot({
  all_running_events %>%
  group_by(school, class_year, date, event) %>%
  summarise(average_time = mean(time, na.rm = TRUE)) %>%  
  mutate(date = mdy(date)) %>%
  mutate(year_date = year(date))|>
  filter( !is.na(.data[[input$categ]])) |>
  ggplot(aes(x = .data[[input$categ]])) +
  geom_bar() +
  labs(x = "Class Year", y = "Average Times")
})
```




Now for field events
```{r}
all_field_events = read_rds("AllFieldEvents.csv")
```





```{r}
library(dplyr)
library(lubridate)
all_jumping_events <- all_jumping_events %>%
  mutate(mark = as.numeric(as.character(mark))) %>%
  group_by(school, class_year, date, event) %>%
  summarise(average_mark = mean(mark, na.rm = TRUE), .groups = 'drop') %>%
  mutate(date = mdy(date), 
         year_date = year(date))
all_jumping_events <- all_jumping_events %>%
  arrange(school, class_year, date)
```








Column 
-------------------------
Now, in the following plots, we are measuring the performance of champions in events that measure their results in meters.

### Select Input
```{r, fig.height=3}
inputPanel(
  selectInput(inputId = "categ3",
              label = h3("Event"),
             choices = c("High Jump","Pole Vault", "Long Jump", "Triple Jump","Shot Put", "Discus", "Hammer", "Javelin"),
              selected = "High Jump"),
  selectInput(inputId = "categ1",
              label = h3("Year"),
              choices = c("2024", "2023", "2022", "2021", "2019", "2018", "2017", "2015"),
              selected = "2024"),
  selectInput(inputId = "categ2",
              label = h3("school"),
              choices = c("Augsburg", "Bethel(Minn.)", "Carleton", "Concordia-Moorhead","Gustavus Adolphus", "Hamline", "Macalester", "Saint Mary's (Minn.)", "St. Benedict", "St. Catherine(Minn.)", "St. Hohn's(Minn.)", "St. Olaf", "St. Scholastica"),
              selected = "Augsburg")
)
```

### The plot for jumping events


```{r, echo=FALSE}
renderPlot({
  all_jumping_events |>
    filter(!is.na(.data[[input$categ]]), year(date) == as.numeric(input$categ1)) |>
    ggplot(aes(x = class_year)) +
    geom_bar() +
    labs(x = "Year", y = "Meters")
})
```
### The plot for Decathlon

```{r}
all_running_events <- all_running_events[!is.na(all_running_events$time), ]
combined_tableDecathlon$points<- as.numeric(as.character(combined_tableDecathlon$points))
```


```{r}
table<-combined_tableDecathlon %>%
  group_by(school, class_year, date) %>%
  summarise(average_points = mean(points, na.rm = TRUE)) %>%  
  arrange(school, class_year, date)|>
   mutate(date = mdy(date)) %>%
    mutate(year_date = year(date))

```



```{r, fig.height=3}
inputPanel(
  selectInput(inputId = "categ1",
              label = h3("Year"),
              choices = c("2024", "2023", "2022", "2021", "2019", "2018", "2017", "2015"),
              selected = "2024"),
  selectInput(inputId = "categ2",
              label = h3("school"),
              choices = c("Augsburg", "Bethel(Minn.)", "Carleton", "Concordia-Moorhead","Gustavus Adolphus", "Hamline", "Macalester", "Saint Mary's (Minn.)", "St. Benedict", "St. Catherine(Minn.)", "St. Hohn's(Minn.)", "St. Olaf", "St. Scholastica"),
              selected = "Augsburg")
)
```


```{r, echo = FALSE}
table <- table |>
  pivot_wider(names_from = school,
              values_from = class_year)
view(table)
```

```{r, echo=FALSE}
renderPlot({
table |>
    ggplot(aes(x = class_year, y = average_points)) +
    geom_bar() +
    labs(x = "calss year", y = "points")
})
```



